Manuscript title here

### 2024-11-01 manuscript.Rmd
La till ATLS tabell

>>>>

| **Parameter**                     | **Class I** | **Class II** (Mild) | **Class III** (Moderate) | **Class IV** (Severe)        |
|-----------------------------------|-------------|----------------------|---------------------------|-------------------------------|
| Approximate blood loss            | <15%        | 15–30%              | 31–40%                    | >40%                          |
| Heart rate                        | ↔           | ↔/↑                 | ↑                         | ↑/↑↑                          |
| Blood pressure                    | ↔           | ↔                   | ↔/↓                       | ↓                             |
| Pulse pressure                    | ↔           | ↓                   | ↓                         | ↓                             |
| Respiratory rate                  | ↔           | ↔                   | ↔/↑                       | ↑                             |
| Urine output                      | ↔           | ↔                   | ↓                         | ↓↓                            |
| Glasgow Coma Scale score          | ↔           | ↔                   | ↓                         | ↓                             |
| Base deficit                      | 0 to –2 mEq/L | –2 to –6 mEq/L     | –6 to –10 mEq/L          | –10 mEq/L or less             |
| Need for blood products           | Monitor     | Possible            | Yes                       | Massive Transfusion Protocol  |
